%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}

\newcommand{\smallplus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\award}[2]{#1 \hfill {\em #2}}

\name{Walker Hildebrand}
% Contact info is in contact-info.tex (git-ignored for privacy)
\input{contact-info.tex}

\begin{document}

\begin{rSection}{Summary}
    \begin{sloppypar}
    Infrastructure engineer specializing in large-scale distributed systems, multi-cloud routing, and high-throughput real-time pipelines. Owned the technical roadmap and architecture for a production CV inference platform sustaining 2~Gbps throughput and 1M$+$ events/day at 99.999996\% uptime across globally distributed fleets. ML inference background from NVIDIA's TensorRT team.
    \end{sloppypar}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

    Go $\cdot$ Python $\cdot$ C++ $\cdot$ SQL $\cdot$ Bazel $\cdot$ Terraform $\cdot$ Kubernetes $\cdot$ AWS $\cdot$ GCP $\cdot$ Docker $\cdot$ OpenTelemetry $\cdot$ Load Balancing \& Request Routing $\cdot$ Networking (L4--7) $\cdot$ Message Queues $\cdot$ Stream Processing $\cdot$ mTLS / Zero-Trust $\cdot$ IaC

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    {\bf University of Waterloo} \hfill 2022 \\
    Bachelor of Computer Science {\em (with Distinction)} \hfill { 88\% Major average}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
    \begin{workexperience}
        {Voxel}
        {Senior Platform Software Engineer}
        {Jan 2023 - Jul 2025}
        {
            \textbf{CV Inference Infrastructure \& High-Throughput Routing:}
            Owned the technical roadmap for Voxel's video inference platform. Architected a multiplexed streaming service as a multi-region, multi-cloud traffic routing layer sustaining 2~Gbps continuous throughput across 2,000 cameras on 150 globally distributed edge devices. Achieved 99.999996\% uptime and 500$+$ req/s with 500~TB under management; routing and queuing improvements cut P95 incident-generation latency by 1$+$ minute at 1M incidents/day scale. Led cross-team design for GDPR-compliant, multi-region, and multi-cloud architecture.

            \vspace{-0.2em}

            Built on-demand transcoding pipeline integrating real-time ML inference for actor anonymization, achieving 1.7s P95 latency while handling bursty traffic peaking at millions of requests/hour; reduced storage COGS 70\% via intelligent non-overlapping fragment strategy.

            \textbf{Cloud-Agnostic Infrastructure \& Geographic Routing:}
            Architected cloud-agnostic edge communication platform on Kubernetes (EKS) with unified ingress and geographic load balancing, eliminating AWS vendor lock-in for enterprise customers. Implemented zero-trust authentication via token provisioning and mTLS with short-lived certificate rotation. Migrated edge telemetry from CloudWatch to self-hosted OpenTelemetry, reducing cloud COGS by 5\%.

            \textbf{Distributed Inference Architecture \& Observability:}
            Designed the data communication layer for Voxel's CV inference pipeline in close collaboration with ML engineers, translating model throughput, batching, and memory requirements into architectural decisions as the system transitioned from single-threaded processes to a horizontally scalable, Flink-based distributed inference architecture.

            \vspace{-0.2em}

            Built data warehouse from ground up using Athena and Glue, establishing observability and performance analytics for distributed inference workloads.

            \textbf{Deployment Infrastructure \& Developer Velocity:}
            Increased deployment velocity 84x by establishing a control plane ecosystem and decoupling config management from the release cycle.

            \vspace{-0.2em}

            Developed widely-adopted Terraform modules with built-in monitoring (SOC~II compliance), standardizing infrastructure provisioning across the engineering organization.

            \textbf{Cross-Functional Leadership:}
            Directly supported Fortune 500 deployments (CVS, FedEx, Chewy) addressing boutique technical requirements to enable initial rollout and unlock expansion. Served as engineering liaison with external contractors supporting IAM and infrastructure migrations.
        }
    \end{workexperience}

    \begin{workexperience}
        {Facebook/Meta}
        {SWE Intern | Network Delivery Systems}
        {Aug 2021 - Dec 2021}
        {
            Built a stream processing pipeline to analyze health across Meta's delivery network at 2~billion events/day, improving signal-to-noise ratio 2.5x and reducing insight latency from hours to seconds.
        }
    \end{workexperience}

    \begin{workexperience}
        {NVIDIA}
        {SWE Intern | TensorRT Inference \& Graph Compiler}
        {Jan 2021 - Apr 2021}
        {
            Contributed to TensorRT~8.0 release on the inference optimization team: developed INT8 quantization accuracy validation for BERT inference on SQuAD, implemented dynamic sequence-length testing pipelines for Tacotron2 + WaveGlow speech synthesis, and resolved release-blocking compiler issues---with direct focus on inference correctness and efficiency trade-offs.
        }
    \end{workexperience}

    \begin{workexperience}
        {NVIDIA}
        {SWE Intern | Hardware Infrastructure}
        {May 2020 - Aug 2020}
        {
            Accelerated CAD tool performance with 6x boot time reduction, developed QuadTree-based spatial algorithms, and contributed OpenGL rendering enhancements across NVIDIA's hardware design suite.
        }
    \end{workexperience}

    \vspace{1em}

\end{rSection}

\end{document}